A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2024-11-24 manuscript/manuscript.qmd
added some tables

library(here)
library(knitr)
library(captioner)

@@

[**Competing Interests Statement:**]{.underline} Dr. Wang has consulted ad hoc for Exponent Inc. and MITRE a federally funded research center for the Centers for Medicare and Medicaid Services on unrelated work. Dr. Schneeweiss is participating in investigator-initiated grants to the Brigham and Women's Hospital from Boehringer Ingelheim, Takeda, and UCB unrelated to the topic of this study. He owns equity in Aetion Inc., a software manufacturer. He is an advisor to Temedica GmbH, a patient-oriented data generation company. His interests were declared, reviewed, and approved by the Brigham and Women's Hospital in accordance with their institutional compliance policies.

@@

@@

::: landscape

# Tables {.unnumbered}

@@

knitr::include_graphics(here("figures", "process.png"))
```

>>>>

library(here)
library(dplyr)
library(knitr)
library(captioner)
library(gt)
library(readxl)

@@

[**Competing Interests Statement:**]{.underline} Dr. Weberpals is now an employee of AstraZeneca and owns stocks in AstraZeneca. Dr. Wang has consulted ad hoc for Exponent Inc. and MITRE a federally funded research center for the Centers for Medicare and Medicaid Services on unrelated work. Dr. Schneeweiss is participating in investigator-initiated grants to the Brigham and Women's Hospital from Boehringer Ingelheim, Takeda, and UCB unrelated to the topic of this study. He owns equity in Aetion Inc., a software manufacturer. He is an advisor to Temedica GmbH, a patient-oriented data generation company. His interests were declared, reviewed, and approved by the Brigham and Women's Hospital in accordance with their institutional compliance policies.

@@

With 21% of all drug approvals, oncology was the disease area with the most FDA drug approvals in 2023.[@senior2024fresh] Although randomized controlled trials (RCTs) are considered the gold standard, decision-makers increasingly rely on real-world evidence (RWE) generated from routine-care health data such as electronic health records (EHR) to evaluate the comparative safety and effectiveness of novel cancer therapies.[@purpura2022role] Especially in the field of precision oncology, RWE has many essential use cases and plays a critical role in complementing evidence like in patient populations that are underrepresented in RCTs, to construct external control arms in single-arm trials where active recruitment may not be feasible or in drug/biomarker discovery and label extensions among pan-tumor populations that harbor specific genomic signatures. However, [to draw causal inferences from such comparisons in non-randomized data, it is pivotal that endpoints and prognostic information can be measured reliably and at scale]{.underline}, which remains a significant challenge in oncological comparative effectiveness research (CER).

@@

::: landscape
# Tables {.unnumbered}

```{r}
#| label: tbl-criteria
#| tbl-cap: "Criteria ."
#| tbl-cap-location: top

eligibility_criteria <- read_excel(
  path = here("tables", "helper_tables.xlsx"),
  sheet = "ctgov_criteria_defintions"
  )

eligibility_criteria |> 
  select(-Link) |> 
  filter(Criteria != "Study phase") |> 
  gt()
```

```{r}
#| label: tbl-rcts
#| tbl-cap: "Tentative list of randomized controlled trials (RCTs) considered for emulation."
#| tbl-cap-location: top

rct_selection <- read_excel(
  path = here("tables", "helper_tables.xlsx"),
  sheet = "rct_selection"
  )

rct_selection |> 
  group_by(cancer) |> 
  gt() |> 
  cols_label(
    nctid = md("**NCTID**"),
    acronym = md("**Acronym**"),
    setting = md("**Clinical setting**"),
    line = md("**Line of therapy**"),
    exposures = md("**Treatment comparison**")
    ) |> 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()
    )
```

@@

knitr::include_graphics(here("figures", "process.png"))

# copy figure to manuscript
# file_copy(
#   path = path, 
#   new_path = here("manuscript", "Figure_2_attrition.png"), 
#   overwrite = TRUE
#   )
```
